%-------------------------
% Resume in Latex
% Author : Vaishnav Mankar
% Based off of: https://github.com/myselfmankar/myselfmankar.github.io
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.6in}
\addtolength{\textheight}{1.2in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-8pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}, itemsep=3pt, topsep=2pt, parsep=0pt, partopsep=0pt]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{-2pt}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in, itemsep=1.5pt, topsep=1.5pt, parsep=0pt, partopsep=0pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-3pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Vaishnav Mukund Mankar} \\ \vspace{1pt}
    \small +91 8668746433 $|$ \href{mailto:vaishnav.mankar04@gmail.com}{\underline{vaishnav.mankar04@gmail.com}} $|$ 
    \href{https://linkedin.com/in/vaishnav-mankar}{\underline{linkedin.com/in/vaishnav-mankar}} $|$
    \href{https://github.com/myselfmankar}{\underline{github.com/myselfmankar}} $|$
    \href{https://myselfmankar.github.io}{\underline{myselfmankar.github.io}}
\end{center}


%-----------SUMMARY-----------
\section{Summary}
  \small{
    Computer Engineering student specializing in backend systems, distributed IoT architectures, and performance optimization. Experienced in Rust, Go, Python, and C++ with expertise in low-latency communication bridges (OCPP, ZMQ, MQTT) and high-throughput data pipelines (gRPC, TimescaleDB, Redis). Adept at orchestrating AI coding agents as a force multiplier under direct human system design control.
  }


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Pune Institute of Computer Technology (PICT)}{Pune, India}
      {B.E. Computer Engineering; \textbf{CGPA: 9.2}}{2023 -- 2027}
    \resumeSubheading
      {Global Public School}{Pune, India}
      {Class XII (HSC); \textbf{Score: 80\%}}{2023}
    \resumeSubheading
      {Ryan International School}{Pune, India}
      {Class X (SSC); \textbf{Score: 90\%}}{2021}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Backend \& Systems Engineer Intern}{May 2026 -- Present}
      {Golain}{Remote/Hybrid}
      \resumeItemListStart
        \resumeItem{Engineered a high-performance EV proxy system in Rust for \textbf{Enough Energy (UK)} to connect physical charging stations with central software utilizing the OCPP-J 1.6 protocol over WebSockets.}
        \resumeItem{Designed a low-latency messaging loop using ZeroMQ (ZMQ) and MQTT to route real-time telemetry, using an embedded Sled DB cache to prevent telemetry data loss during temporary network drops.}
        \resumeItem{Leveraged AI-agent workflows to generate boilerplate and test suites under direct system design control, accelerating deployment speed while owning database schemas, query optimizations, and container orchestration.}
      \resumeItemListEnd

    \resumeSubheading
      {Freelance Full-Stack Developer \& Agent Operator}{April 2026}
      {Independent}{Pune, India}
      \resumeItemListStart
        \resumeItem{Built a student performance analytics dashboard for investor presentations, integrating physical pen-tech hardware telemetry (CAN/Modbus sensors) with a preprocessed backend data pipeline using React, TypeScript, and Firebase.}
        \resumeItem{Designed dynamic KPI charts, visualizations, and client-side AI summarizers to provide real-time strengths, weaknesses, and writing dynamics analysis.}
        \resumeItem{Managed AI coding agents to rapidly scaffold UI components and routing, focusing manual cognitive effort on system schema, database design, and hardware-software data mapping.}
      \resumeItemListEnd

    \resumeSubheading
      {AI Developer Intern}{Aug 2025 -- May 2026}
      {Banao.tech}{Remote}
      \resumeItemListStart
        \resumeItem{Engineered backend components for an AI-driven EdTech video generation pipeline, automating personalized multilingual video creation from images and textual summaries.}
        \resumeItem{Learned and applied python-langchain, GitHub workflows, AWS Lambda serverless execution, and cloud logging telemetry to optimize execution and debug latency.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{FieldPulse (Industrial IoT Backend Platform)}}{Tech Stack: Go, gRPC, TimescaleDB, Redis, MQTT, OpenTelemetry (OTLP)}
          \resumeItemListStart
            \resumeItem{Developed a distributed industrial IoT telemetry ingestion backend in Go, utilizing gRPC microservices and TimescaleDB hypertables.}
            \resumeItem{Optimized database storage using TimescaleDB time-partitioning, automatic 7-day compression (~90\% savings), and data retention policies.}
            \resumeItem{Integrated Redis for sensor telemetry deduplication and alert suppression, and instrumented all services with OpenTelemetry to trace across HTTP, gRPC, and MQTT boundaries.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{AI-Powered Smart Photo Gallery (digital-asset-management)}}{Tech Stack: React, FastAPI, PostgreSQL, Gemini, Docker}
          \resumeItemListStart
            \resumeItem{Engineered a private, local-first "Google Photos" alternative allowing natural language search queries on unstructured media, implementing AI-driven semantic image tagging and text-to-SQL search query optimizations.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------ACHIEVEMENTS-----------
\section{Achievements}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{IEEE Publication:} Published "GNN-Based Friend Recommendation: A Graph Embedding Approach for Social Networks" in an IEEE International Conference.
    }}
 \end{itemize}


%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Rust, Go, Python, C++, SQL, TypeScript, JavaScript} \\
     \textbf{Frameworks}{: FastAPI, React, Next.js, LangChain, ZeroMQ, gRPC} \\
     \textbf{Cloud \& Tools}{: AWS, Docker, Git, Linux, TimescaleDB, PostgreSQL, Redis, Firebase, OpenTelemetry (OTLP)} \\
     \textbf{Concepts}{: Data Structures \& Algorithms (DSA), Operating Systems (OS), Database Management Systems (DBMS), Computer Networks (CN), Object-Oriented Programming (OOP), Concurrency, System Design, IoT Protocols (OCPP, MQTT)}
    }}
 \end{itemize}



%-------------------------------------------
\end{document}